### 2020-04-20 papers-vol-1.tex
Add keynote
updated titles vol 1

\insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/1longAakhus.docx.pdf}
\insertmydocument{chapter}{What is Wrong with Deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}

@@

\insertmydocument{chapter}{Critical discussion for sub-optimal settings}{Diego Castro}{pdfs/long/7longCastro.doc.pdf}
\insertmydocument{chapter}{Comments on Diego Castro’s Critical Discussion in Sub-Optimal Settings}{David Godden}{pdfs/commentary/7longCastro-C.doc.pdf}

@@

\insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s Strength of Reasons for Moral Dissent}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}

\insertmydocument{chapter}{Where Are Dissent and Reasons in Epistemic Justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
\insertmydocument{chapter}{Knowledge and the Epistemic Function of Argumentation -- Commentary on Gasc\'{o}n's Where Are dissent and Reasons in Epistemic Justification?}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}

\insertmydocument{chapter}{Justifying Questions?}{G.C. Goddu}{pdfs/long/11LongGoddu.doc.pdf}
\insertmydocument{chapter}{Commentary on G. C. Goddu’s Justifying Questions?}{David Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}

@@

\insertmydocument{chapter}{Grice, Machine Head and the Problem of Overexpressed Premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
\insertmydocument{chapter}{Commentary on Hoppmann’s Grice, Machine Head and the Problem of Overexpressed Premises}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}

\insertmydocument{chapter}{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{Sally Jackson, Scott Jacobs, Xiaoqi Zhang}{pdfs/long/16longJackson.doc.pdf}
\insertmydocument{chapter}{A wanting analysis -- Commentary on S. Jackson, S. Jacobs, Y. Zhang's Standpoints and Commitments as Products of Argumentative Work: Micro/Macro-Analysis of an Infamous Press Conference}{Harald R. Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}

@@

\insertmydocument{chapter}{Visual and Auditory Schemes of Argument}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing Adbusters’ Spoofing Strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.docx.pdf}
\insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
\insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
\insertmydocument{chapter}{With All Due Respect: Controversial Beliefs and the Limits of Responsible Argumentation}{Tracy Bowell}{pdfs/thematic/7regularThematicBowell.doc.pdf}
\insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
\insertmydocument{chapter}{From Dialogic to Argument-based Teaching: Significant Teacher Moves in Framing Classroom-based Argumentation Dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}

>>>>

\insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/1longAakhus.docx.pdf}

\insertmydocument{chapter}{Revisiting Apologie de la Polémique: Coexistence in Dissent and its “Felicity Conditions”}{Ruth Amossy}{pdfs/keynote/1keynoteAmossy.doc.pdf}

\insertmydocument{chapter}{What is Wrong with Deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}

@@

\insertmydocument{chapter}{Critical discussion for sub-optimal settings}{Diego Castro}{pdfs/long/7longCastro.doc.pdf}
\insertmydocument{chapter}{Comments on Diego Castro’s ``Critical Discussion in Sub-Optimal Settings''}{David Godden}{pdfs/commentary/7longCastro-C.doc.pdf}

@@

\insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s ``Strength of Reasons for Moral Dissent''}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}

\insertmydocument{chapter}{Where Are Dissent and Reasons in Epistemic Justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
\insertmydocument{chapter}{Knowledge and the Epistemic Function of Argumentation -- Commentary on Gasc\'{o}n's ``Where Are dissent and Reasons in Epistemic Justification?''}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}

\insertmydocument{chapter}{Justifying Questions?}{G.C. Goddu}{pdfs/long/11LongGoddu.doc.pdf}
\insertmydocument{chapter}{Commentary on G. C. Goddu’s ``Justifying Questions?''}{David Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}

@@

\insertmydocument{chapter}{Grice, Machine Head and the Problem of Overexpressed Premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
\insertmydocument{chapter}{Commentary on Hoppmann’s ``Grice, Machine Head and the Problem of Overexpressed Premises''}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}

\insertmydocument{chapter}{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{Sally Jackson, Scott Jacobs, Xiaoqi Zhang}{pdfs/long/16longJackson.doc.pdf}
\insertmydocument{chapter}{A wanting analysis -- Commentary on S. Jackson, S. Jacobs, Y. Zhang's ``Standpoints and Commitments as Products of Argumentative Work: Micro/Macro-Analysis of an Infamous Press Conference''}{Harald R. Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}

@@

\insertmydocument{chapter}{Visual Argument Schemes in the PTA}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing the Spoofing Strategies in Subvertisements of the Tobacco Industry
}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.docx.pdf}
\insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
\insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
\insertmydocument{chapter}{With All Due Respect: Controversial Beliefs and the Limits of Responsible Argumentation}{Tracy Bowell}{pdfs/thematic/7regularThematicBowell.doc.pdf}
\insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
\insertmydocument{chapter}{From Dialogic to Argument-Based Teaching: Introducing Pragmatic Criteria to Analyse Whole-Class Interactions}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}
